---
title: "minimizR with Template Model Builder"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About Template Model Builder

Template Model Builder is a framework that uses Automatic Differentiation to fit models to data. More information can be found at <https://cran.r-project.org/web/packages/TMB/index.html>. 

## R Code Using minimizR with TMB

Below is the TMB thetalog example using minimizR. The original code can be found at <https://github.com/kaskr/adcomp/tree/master/tmb_examples>.

```{r tmb}
library(minimizR)
library(TMB)
compile("tmb_src/thetalog.cpp")
dyn.load(dynlib("tmb_src/thetalog"))

## Read data
Y <- scan("tmb_src/thetalog.dat", skip=3, quiet=TRUE)
data <- list(Y=Y)

## Parameter initial guess
parameters <- list(
  X = data$Y*0,
  logr0 = 0,
  logtheta = 0,
  logK = 6,
  logQ = 0,
  logR = 0
)

## Create the AD Function
obj <- MakeADFun(data, parameters, random="X", DLL="thetalog", silent = TRUE)
newtonOption(obj, smartsearch=FALSE)
```

## Initial Function Value And Gradient

```{r tmb2}
obj$fn()
obj$gr()
```

## Run The Minimizer and View The Results

```{r tmb3}
#Fit the model
opt <- minimizR::minimize(obj$par, obj$fn, obj$gr)
print(opt)
```

## View The SD Report From TMB

```{r tmb4}
rep <- sdreport(obj)
print(rep)

```
