---
title: "minimizR"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## minimizR

minimizR is a l-bfgs function minimizer that works with freely estimable or value bounded parameter sets.

## Freely Estimated Example

Here is an example of minimizing the Rosenbrock function with freely estimated parameters.

```{r min}
library(minimizR)

#Rosenbrock function
objective <- function(x) {
  return( 100 * (x[2] - x[1] * x[1])^2 + (1 - x[1])^2 )
}

#Rosenbrock gradient function
gradient <- function(x) {
  return( c( -400 * x[1] * (x[2] - x[1] * x[1]) - 2 * (1 - x[1]), 200 * (x[2] - x[1] * x[1]) ) )
}

#estimated parameters
x<-c(-1.2, 0)

#minimizR minimizer function
opt<-minimizR::minimize(x,                    #initial parameters values
                        objective,            #objective function
                        gradient,             #gradient function
                        control = list(       #control list
                        tolerance = 1e-5,     #convergence criteria
                        verbose = TRUE,       #print status
                        iprint = 10))         #print interval

```

## Output

```{r out}
print(opt)
```

## Value Bounded Example

Here is an example of minimizing the Rosenbrock function with value bounded parameters. Note: if "minb" and "maxb" are omitted from the control list, all parameters will be freely estimated.

```{r minb}
library(minimizR)

#Rosenbrock function
objective <- function(x) {
  return( 100 * (x[2] - x[1] * x[1])^2 + (1 - x[1])^2 )
}

#Rosenbrock gradient function
gradient <- function(x) {
  return( c( -400 * x[1] * (x[2] - x[1] * x[1]) - 2 * (1 - x[1]), 200 * (x[2] - x[1] * x[1]) ) )
}

#estimated parameters
x<-c(-1.2, 0)

#minimizR minimizer function
opt<-minimizR::minimize(x,                    #initial parameters values
                        objective,            #objective function
                        gradient,             #gradient function
                        control = list(       #control list
                        tolerance = 1e-8,     #convergence criteria
                        minb = c(-1.5, -1.5), #min bounds
                        maxb = c(1.5,1.5),    #max bounds
                        verbose = TRUE,       #print status
                        iprint = 10))         #print interval

```

## Output

```{r outb}
print(opt)
```
