---
title: "minimizR with TMB"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About Template Model Builder

Template Model Builder is a framework that uses Automatic Differentiation to fit models to data.More information can be found at https://github.com/kaskr/adcomp.

## R Code Using miniimizR with TMB

Below is the TMB thetalog example using minimizR. The original code can be found at https://github.com/kaskr/adcomp/tree/master/tmb_examples.

```{r tmb}
library(minimizR)
library(TMB)
compile("tmb_src/thetalog.cpp")
dyn.load(dynlib("tmb_src/thetalog"))

## Read data
Y <- scan("tmb_src/thetalog.dat", skip=3, quiet=TRUE)
data <- list(Y=Y)

## Parameter initial guess
parameters <- list(
  X = data$Y*0,
  logr0 = 0,
  logtheta = 0,
  logK = 6,
  logQ = 0,
  logR = 0
)

## Create the AD Function
obj <- MakeADFun(data, parameters, random="X", DLL="thetalog", silent = TRUE)
newtonOption(obj, smartsearch=FALSE)
```
## Initial function value and gradient
```{r tmb2}
obj$fn()
obj$gr()
```

## Run the minimizer and view the results
```{r tmb3}
#Fit the model
opt <- minimizR(obj$par, obj$fn, obj$gr)
print(opt)
```
## View the SD Report
```{r tmb4}
rep <- sdreport(obj)
print(rep)

```

